Distributional Trees for Circular Data

### 2019-06-28 pkg/disttree/inst/IWSM2019/abstract_IWSM2019_schlosser.tex
first draft of slides for IWSM 2019
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2626 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 227c0bb756d4097710ef42ed50c0b6a74658c2bd

\subsection{Ensembles and random forests}
A natural extension are ensembles or forests of such circular trees
that can improve forecasts by regularizing and stabilizing the model.
Random forests introduced by Breiman~et.~al~(1984) average the
predictions of an ensemble of trees, each built on a subsample 
or bootstrap of the original data. 
A generalization of this strategy is to obtain weighted predictions
by adaptive local likelihood estimation of the distributional parameters
(Schlosser~et.~al, 2019). More specifically, for each possibly new
observation~$x$ a set of ``nearest neighbor'' weights $w_i(x)$ is obtained 
that is based on how often $x$ is assigned to the same terminal node as
each learning observation $y_i, i \in \{1,\ldots,n\}$.

@@

\item[Breiman, L., Friedman, J. H., Olshen, R. A., and Stone, C. J.] (1984).
     Classification and Regression Trees.
     {\it Wadsworth}.

@@

\item[Jammalamadaka, S. R. and Sengupta, A.] (2001).
     {\it Topics in Circular Statistics}.
     World Scientific.

@@

\item[Schlosser, L., Hothorn, T., and Zeileis, A.] (2019).
     Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain.
     arXiv:1804.02921, {\it arXiv.org E-Print Archive}.

>>>>

\subsection{Ensembles and random forests}
A natural extension are ensembles or forests of such circular trees
that can improve forecasts by regularizing and stabilizing the model.
Random forests introduced by Breiman~(2001) average the
predictions of an ensemble of trees, each built on a subsample 
or bootstrap of the original data. 
A generalization of this strategy is to obtain weighted predictions
by adaptive local likelihood estimation of the distributional parameters
(Schlosser~et.~al, 2019). More specifically, for each possibly new
observation~$x$ a set of ``nearest neighbor'' weights $w_i(x)$ is obtained 
that is based on how often $x$ is assigned to the same terminal node as
each learning observation $y_i, i \in \{1,\ldots,n\}$.

@@

\item[Breiman, L.] (2001).
     Random Forests.
     {\it Machine Learning}, {\bf 45}, 1,
     5\,--\,32.

@@

\item[Jammalamadaka, S. R., and Sengupta, A.] (2001).
     {\it Topics in Circular Statistics}.
     World Scientific.

@@

\item[Schlosser, L., Hothorn, T., Stauffer, R., and Zeileis, A.] (2019).
     Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain.
     arXiv:1804.02921, {\it arXiv.org E-Print Archive}.
